---
title: "Overview"
author: "Atef Chaudhury, Aiden Lee, Yogi Joshi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## How to Use

 * Run parse.py in the ragel directory 
 * Input timed-regular expression in the appropriate format (as described in the following section)
 * View a diagram of the newly generated automaton by running ragel_graph.py, if desired
 * Rebuild the R-package ensuring that the cpp code is recompiled
 * Call processTrace as follows

```{r}
library(automatonR)
library(Rcpp)
traceTimes = c(0, 2, 3, 5, 7)
traceEvents = c(1, 2, 2, 1, 2)
alphabetLength = 2

# The last parameter here is used for the hard coded automaton: (<0.1> | <1.0>)+
# If using the parser generated automaton, leave parameter blank
result = processTrace(traceTimes, traceEvents, alphabetLength, "(<0.1> | <1.0>)+")
result
```


The result for a specific alphabet configuration can be accessed as follows:

```{r}
result$success[1,2]
```

## Input format

The timed regular expression must be input with the following format

 * All expressions must be concatenated with the '.' operator ( 0.1 instead of 01 )
 * The elements of the regex must only be the natural numbers
   from 0 to n with no gaps ( 1.0.2 instead of 1.0.3 or 8.9.3 )
 * Timed intervals are indicated with <> (ex. <0.1>)
 * Parenthesis are required when using the + or * operator on a timed interval
   ( (<0.1>)+ instead of <0.1>+ )
  
The function processTrace also has the following assumptions

 * All traces start at t=0
 * All trace events are only natural numbers from 1 to the alphabetLength




